---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# DDHQA WALKTHROUGH
This package automates different quality checks for the World Bank's Data Catalog

The Data Catalog is organized into datasets corresponding resources, each category has a different set of QA checks. Each check returns a PASS/FAIL status and a detailed message of the results.

### Set up
First, install the package from GitHub.
```{r eval = FALSE}
devtools::install_github(package = "tonyfujs/ddhqa")
```

Next, run your Data Catalog credentials.
```{r eval = FALSE}
url <- 'https://datacatalog.worldbank.org/'
username <- 'USERNAME'
password <- 'PASSWORD'
credentials <- dkanr::dkanr_setup(url, username, password)
```

## Dataset Checks
For checking datasets, locate the nid for the given dataset and save its metadata.
```{r eval = FALSE}
dataset_metadata <- ddhconnect::get_metadata(nid = "94645")
```

Depending on the type of dataset (Microdata, Geospatial, Time Series), there are different recommended fields to include. The `check_recom_fields()` function assess the dataset's metadata and returns a list of missing recommended fields if the test fails.  
```{r eval = FALSE}
check_recom_fields(dataset_metadata)
```

Each dataset is required to have a corresponding resource. The `check_missing()` function if a dataset lacks a resource.  
```{r eval = FALSE}
check_missing(dataset_metadata)
```

Some datasets have an embargo date. If the embargo date is before the current date, the `check_embargo_date()` function will flag the dataset.
```{r eval = FALSE}
check_embargo_date(dataset_metadata)
```

## Resource Checks
For checking resources, locate the nid for the given resource and save its metadata.
```{r eval = FALSE}
dataset_nid <- "94645"
resource_nids <- ddhconnect::get_resource_nid(dataset_nid)
resource_metadata <- ddhconnect::get_metadata(resource_nids[[1]])
```

To check the resource's extension with the form's field value (such as XLSX, CSV, etc.), use the `check_file_ext()` function. This assesses the following:
* contains `field_format` but is missing a path with the expected file extension
* contains valid file extension but unpopulated field_format
* field_format and file extension do not match
```{r eval = FALSE}
check_file_ext(resource_metadata)
```

To check for a valid/active link and 404 errors, use the 'check_resource_link()' function.
```{r eval = FALSE}
check_resource_link(resource_metadata)
```

Sometimes, datasets will have unpublished resources (issue arose due to harvesting). Use the `check_unpublished()` function to see if the resource is published.
```{r eval = FALSE}
check_unpublished(resource_metadata)
```

Some datasets are confidential or official-use only. Use the `check_privacy_status()` function to ensure the associated resource has the same setting.
```{r eval = FALSE}
# NOTE: still in progress
dataset_metadata <- ddhconnect::get_metadata(dataset_nid)
data_class_tid <- unlist(dataset_metadata[["field_wbddh_data_class"]], use.names = FALSE)
data_class_ui <- lovs[lovs$tid == data_class_tid & lovs$machine_name == "field_wbddh_data_class", ]$list_value_name

if (data_class_ui == "Public") {
  check_privacy_status(resource_metadata)
}
```

Use `check_file_path()` to check if the resources have the correct path based on data classification.
```{r eval = FALSE}
check_file_path(resource_metadata)
```

## Other checks
`check_overall()`

### checking frequency of metadata fields
Call `count_machine_names()` to have a better understanding to see which metadata fields are used.
These results are will display the frequency of use as well as frequency of the field being empty (null or empty list).
```{r eval = FALSE}
# datasets
count_machine_names(datasets)

# resources
count_machine_names(resources)
```
