---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# DDHQA WALKTHROUGH
This package automates different quality checks for the World Bank's Data Catalog

## Set up
```{r setup, include = FALSE}
package <- 'tonyfujs/ddhconnect'
github_token <- '***REMOVED***'
httr::set_config(httr::config(ssl_verifypeer = 0L))
devtools::install_github(package, auth_token = github_token)
)
```

run credentials
```{r setup, include = FALSE}
url <- 'https://datacatalog.worldbank.org/'
username <- '***REMOVED***'
password <- '***REMOVED***'
credentials <- dkanr::dkanr_setup(url, username, password)
```

## GENERAL WORK FLOW
1. Gather all metadata [datasets/resources]
2. Field names being used/unused [datasets/resources]
3. File extension match listed type [resources]
4. External links are valid/check 404 [resources]

### [ 1 ] gather all metadata
NOTE: need to allow for a subset, maybe make get_metadata a public function
also need to come up with a better name
In order to run the other analyses, you need metadata data for a subset of all of the datasets or resources.
```{r setup, include = FALSE}
# datasets
get_metadata_datasets()
# resources
get_metadata_resources()
```

You can also take a subset by searching the catalog and passing the nids
### [ 2 ] checking machine names
```{r setup, include = FALSE}
count_machine_names()
```

### [ 3 ] file extensions
```{r setup, include = FALSE}
```



### [ 4 ] external links
```{r setup, include = FALSE}
```

### [ 5 ] missing recommended fields

## Shiny view
